MATLAB Distributed Compute on \CNAME

### 2016-03-02 matlab_dcs_101/paper.tex
added info on the optional parameter

\subsection{Importing \CNAME~MATLAB profile}
\begin{frame}
  \frametitle{Cluster Profile Setup}
  \begin{picture}(320,250)
    \onslide<1,3->{\put(-8,92){\includegraphics[width=0.8\linewidth]{screenshots/set_path_button}}}
    \only<1>{\put (126,232){\begin{tikzpicture}\draw[red,thick,solid] (0,0) -- (0.6,0) -- (0.6,0.2) -- (0,0.2) -- (0,-0.01);\end{tikzpicture}}}
    \onslide<2>{\put(-8,92){\includegraphics[width=0.8\linewidth]{screenshots/manage_profile}}}
    \only<2>{\put (128,214){\begin{tikzpicture}\draw[red,thick,solid] (0,0) -- (1,0) -- (1,0.2) -- (0,0.2) -- (0,-0.01);\end{tikzpicture}}}
    \onslide<3-4>{\put(-8,92){\includegraphics[width=0.4\linewidth]{screenshots/CPM_1}}}
    \only<3>{\put (9.2,163.5){\begin{tikzpicture}\draw[red,thick,solid] (0,0) -- (0.3,0) -- (0.3,0.46) -- (0,0.46) -- (0,-0.01);\end{tikzpicture}}}
    \onslide<4>{\put(55,135){\includegraphics[width=0.35\linewidth]{screenshots/CPM_2}}}
    \only<4>{\put (57,165){\begin{tikzpicture}\draw[red,thick,solid] (0,0) -- (1.5,0) -- (1.5,0.2) -- (0,0.2) -- (0,-0.01);\end{tikzpicture}}}
    \only<4>{\put (133.5,136.5){\begin{tikzpicture}\draw[red,thick,solid] (0,0) -- (0.7,0) -- (0.7,0.22) -- (0,0.22) -- (0,-0.01);\end{tikzpicture}}}
    \onslide<5,9>{\put(-8,92){\includegraphics[width=0.4\linewidth]{screenshots/CPM_3}}}
    \only<5>{\put (-8.2,149.65){\begin{tikzpicture}\draw[red,thick,solid] (0,0) -- (1.15,0) -- (1.15,0.15) -- (0,0.15) -- (0,-0.01);\end{tikzpicture}}}
    \only<5>{\put (115.6,92.4){\begin{tikzpicture}\draw[red,thick,solid] (0,0) -- (0.4,0) -- (0.4,0.16) -- (0,0.16) -- (0,-0.01);\end{tikzpicture}}}
    \onslide<6>{\put(-8,92){\includegraphics[width=0.8\linewidth]{screenshots/CPM_4}}}
    \onslide<7>{\put(-8,92){\includegraphics[width=0.8\linewidth]{screenshots/CPM_4}}}
    \onslide<8>{\put(-8,92){\includegraphics[width=0.8\linewidth]{screenshots/CPM_4}}}
    \put(-20,82){
      \begin{minipage}[t]{0.95\linewidth}
        {
          \only<1>{\normalsize{Click the ``\textbf{Parallel}'' button to bring up the Parallel drop down menu}}
          \only<2>{\normalsize{Select \textbf{Manage Cluster Profiles} in the Parallel drop down menu }}
          \only<3>{\normalsize{In the \textbf{Cluster Profile Manager} dialogue box, click on\\the ``\textbf{Import}'' icon}}
          \only<4>{\normalsize{Navigate to and \textbf{Open} the uhhpc-matlab.settings file\\that was downloaded}}
          \only<5>{\normalsize{Select the \textbf{uhhpc} cluster profile, and press the ``\textbf{Edit}'' button.\\For ease of editing, you may want to increase the window size}}
          \only<6>{\footnotesize{Each of the functions in the \textbf{SUBMIT FUNCTIONS} section, have the follow format:}\\
            \textbf{\tiny{\{`$<$func$>$',`$<$server addr$>$', `$<$remote storage dir$>$', `$<$slurm partition$>$', `$<$slurm timelimit$>$'\}} } 
          }
          \only<7>{\normalsize{\textbf{\tiny{\{`$<$func$>$',`$<$server addr$>$', `$<$remote storage dir$>$', `$<$slurm partition$>$', `$<$slurm timelimit$>$'\}}}\\Replace the remote storage dir with the path that matches your users lus folder location i.e., /home/$<$username$>$/lus/}}
          \only<8>{\normalsize{\textbf{\tiny{\{`$<$func$>$',`$<$server addr$>$', `$<$remote storage dir$>$', `$<$slurm partition$>$', `$<$slurm timelimit$>$'\}}}\\Adjust the slurm partition and slurm timelimit to fit the partition you wish to run on, and finally click \textbf{done}}}
					\only<9>{\normalsize{The profile should now be configured for your user on \CNAME }}
        }
      \end{minipage}
    }
  \end{picture}
\end{frame}

>>>>

\subsection{Importing \CNAME~MATLAB profile}
\begin{frame}
  \frametitle{Cluster Profile Setup}
  \begin{picture}(320,250)
    \onslide<1,3->{\put(-8,92){\includegraphics[width=0.8\linewidth]{screenshots/set_path_button}}}
    \only<1>{\put (126,232){\begin{tikzpicture}\draw[red,thick,solid] (0,0) -- (0.6,0) -- (0.6,0.2) -- (0,0.2) -- (0,-0.01);\end{tikzpicture}}}
    \onslide<2>{\put(-8,92){\includegraphics[width=0.8\linewidth]{screenshots/manage_profile}}}
    \only<2>{\put (128,214){\begin{tikzpicture}\draw[red,thick,solid] (0,0) -- (1,0) -- (1,0.2) -- (0,0.2) -- (0,-0.01);\end{tikzpicture}}}
    \onslide<3-4>{\put(-8,92){\includegraphics[width=0.4\linewidth]{screenshots/CPM_1}}}
    \only<3>{\put (9.2,163.5){\begin{tikzpicture}\draw[red,thick,solid] (0,0) -- (0.3,0) -- (0.3,0.46) -- (0,0.46) -- (0,-0.01);\end{tikzpicture}}}
    \onslide<4>{\put(55,135){\includegraphics[width=0.35\linewidth]{screenshots/CPM_2}}}
    \only<4>{\put (57,165){\begin{tikzpicture}\draw[red,thick,solid] (0,0) -- (1.5,0) -- (1.5,0.2) -- (0,0.2) -- (0,-0.01);\end{tikzpicture}}}
    \only<4>{\put (133.5,136.5){\begin{tikzpicture}\draw[red,thick,solid] (0,0) -- (0.7,0) -- (0.7,0.22) -- (0,0.22) -- (0,-0.01);\end{tikzpicture}}}
    \onslide<5,9>{\put(-8,92){\includegraphics[width=0.4\linewidth]{screenshots/CPM_3}}}
    \only<5>{\put (-8.2,149.65){\begin{tikzpicture}\draw[red,thick,solid] (0,0) -- (1.15,0) -- (1.15,0.15) -- (0,0.15) -- (0,-0.01);\end{tikzpicture}}}
    \only<5>{\put (115.6,92.4){\begin{tikzpicture}\draw[red,thick,solid] (0,0) -- (0.4,0) -- (0.4,0.16) -- (0,0.16) -- (0,-0.01);\end{tikzpicture}}}
    \onslide<6>{\put(-8,92){\includegraphics[width=0.8\linewidth]{screenshots/CPM_4}}}
    \onslide<7>{\put(-8,92){\includegraphics[width=0.8\linewidth]{screenshots/CPM_4}}}
    \onslide<8>{\put(-8,92){\includegraphics[width=0.8\linewidth]{screenshots/CPM_4}}}
    \put(-20,82){
      \begin{minipage}[t]{0.95\linewidth}
        {
          \only<1>{\normalsize{Click the ``\textbf{Parallel}'' button to bring up the Parallel drop down menu}}
          \only<2>{\normalsize{Select \textbf{Manage Cluster Profiles} in the Parallel drop down menu }}
          \only<3>{\normalsize{In the \textbf{Cluster Profile Manager} dialogue box, click on\\the ``\textbf{Import}'' icon}}
          \only<4>{\normalsize{Navigate to and \textbf{Open} the uhhpc-matlab.settings file\\that was downloaded}}
          \only<5>{\normalsize{Select the \textbf{uhhpc} cluster profile, and press the ``\textbf{Edit}'' button.\\For ease of editing, you may want to increase the window size}}
          \only<6>{\footnotesize{Each of the functions in the \textbf{SUBMIT FUNCTIONS} section, have the follow format:}\\
            \textbf{\tiny{\{$<$func$>$,`$<$server addr$>$', `$<$remote storage dir$>$', `$<$partition$>$', `$<$timelimit$>$', [$<$mem usage in MB$>$] \} } }
          }
          \only<7>{\normalsize{\textbf{\tiny{\{`$<$func$>$',`$<$server addr$>$', `$<$remote storage dir$>$', `$<$partition$>$', `$<$timelimit$>$', [$<$mem usage in MB$>$] \}}}\\Replace the remote storage dir with the path that matches your users lus folder location i.e., /home/$<$username$>$/lus/}}
          \only<8>{\normalsize{\textbf{\tiny{\{`$<$func$>$',`$<$server addr$>$', `$<$remote storage dir$>$', `$<$partition$>$', `$<$timelimit$>$', [$<$mem usage in MB$>$] \}}}\\Adjust the slurm partition and slurm timelimit to fit the partition you wish to run on, and finally click \textbf{done}}}
					\only<9>{\normalsize{The profile should now be configured for your user on \CNAME }}
        }
      \end{minipage}
    }
  \end{picture}
\end{frame}
